---
title: "script"
author: "Yuri Kulchisky"
date: "25.01.2015"
output:
  html_document

---

### Loading packages
```{r}
library(data.table)
library(reshape2)
```

### Getting data

At first, we well download and unzip file in case if it is not done before.

```{r, message=FALSE}
url <- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
fname <- "Dataset.zip"
if (!file.exists(fname)) download.file(url, file.path(getwd(), fname),method="wget")
if (!file.exists("UCI HAR Dataset/")) unzip(fname)
```

### Basic summary

We can discover features of this dataset by reading the file named *README.TXT*. The information about features is in the file named *features_info.txt*. We need to use only cleared signal, which means, that we ignore *Inertial Signals* folder. The training dataset has the next structure: rows in file named *subject_test.txt* contain the code numbers of 24 subjects, the rows in file *y_test.txt* contain the type of activity, and rows in file *X_test.txt* contain data. The testing dataset is organized in the same way.

The important thing is that *features.txt* contains the list of all features, from which only mean and standard deviation are of interest for us.

```{r}
features <- as.vector(read.table(file="UCI HAR Dataset/features.txt",col.names=c("","f"))[2][[1]])

subject_test <- data.table(read.table(file="UCI HAR Dataset/test/subject_test.txt"))
subject_train <- data.table(read.table(file="UCI HAR Dataset/train/subject_train.txt"))

data_test <- data.table(read.table(file="UCI HAR Dataset/test/X_test.txt",sep=""))
setnames(data_test,features)

data_train <- data.table(read.table(file="UCI HAR Dataset/train/X_train.txt",sep=""))
setnames(data_train,features)

activities <- data.table(read.table(file="UCI HAR Dataset/activity_labels.txt",col.names=c("","f")))

activities_test <- data.table(read.table(file="UCI HAR Dataset/test/y_test.txt"))
activities_train <- data.table(read.table(file="UCI HAR Dataset/train/y_train.txt"))
```

## Merging datasets

After merging datasets we select needed features by using regular expressions mechanism to delete variables that will not be used.
```{r}
merged_data <- rbind(data_train,data_test)
merged_subject <- rbind(subject_train,subject_test)
merged_activities <- rbind(activities_train,activities_test)

needed_features <- c(grep("+mean[[:punct:]]+",features),grep("+std[[:punct:]]+",features))
cleaned_data <- merged_data[,needed_features,with=FALSE]
```

```{r}
data_frame <- cbind(merged_subject,merged_activities)
setnames(data_frame,c("Subject","Activity_code"))
setnames(activities,c("Activity_code","Activity"))
data_frame <- merge(data_frame, activities, by = "Activity_code", all.x = TRUE)
data_frame[,Activity_code:=NULL]
data_frame <- cbind(data_frame,cleaned_data)
setnames(data_frame,c("Subject","Activity",features[needed_features]))
setkey(data_frame, Subject, Activity)
```

The main dataset was created. Now let's go to the process of evaluating tidy dataset.

```{r}
x <- data_frame
n <- as.numeric(levels(factor(x$Subject)))
act <- levels(factor(x$Activity))
tidy <- as.data.frame(matrix(rep(1:length(colnames(x)),length(n)),nrow=length(n)))
colnames(tidy)<- colnames(x)
ft <- colnames(x)[3:length(colnames(x))]
for (k in 1:length(ft)){
  for (i in 1:length(n)) {
    for (j in 1:length(act)){
      xrow <- x[x$Subject==i]
      xrow1 <- xrow[xrow$Activity==act[j]]
      eval(parse(text=paste0("tidy$\'",ft[k],"\'[i]<-mean(xrow1$\'",ft[k],"\')")))
    }
  }
}

write.table(tidy,file="tidy.txt",row.names=FALSE)

```








